\section{Introduction}
This section contains a brief introduction to the \textbf{P}roject \textbf{P}lan \textbf{D}ocument.
%
\subsection{Purpose and Scope}
%TODO State the purpose and scope of the document
The purpose of this document is to explain the Project Plan devised for the system to be.
All the people involved in the project could be considered as possible readers of the document, but the document itself is more of a guide for the Project Manager and the Management in general.
The Project Plan consists in tables, Gantt diagrams, charts and natural language descriptions of the planning, scheduling and management of \myTaxiService{} development.
%
\subsection{List of Definitions and Abbreviations}
In the document are often used some technical terms whose definitions are here reported:
\begin{itemize}
	%TODO Aggiungere
	\item See the correspondent section in the \textbf{RASD} for more definitions.
\end{itemize}
For sake of brevity, some acronyms and abbreviations are used:
\begin{itemize}
	\itemBold{PPD} Project Plan Document.
	\itemBold{FP} Function Points.
	\itemBold{ILF} Internal Logic File.
	\itemBold{ELF} External Logic File.
	\itemBold{EI} External Input.
	\itemBold{EO} External Output.
	\itemBold{EIQ} External Inquiry.
	\itemBold{COCOMO} Constructive Cost Model.
	%TODO Aggiungere
	\item See the correspondent section in the \textbf{RASD} for more acronyms and abbreviations.
\end{itemize}
%
\subsection{List of Reference Documents}
\begin{itemize}
	\itemBold{\myTaxiService{} RASD v1.3} Requirements Analysis and Specification Document
	%\itemBold{\myTaxiService{} DD v1.1} Design Document
	%\itemBold{\myTaxiService{} ITPD v1.0} Integration Test Plan Document
	\itemBold{Assignment 5 - Project Plan} Project Plan specification document
	\itemBold{COCOMO II - Model Definition Manual} \href{http://csse.usc.edu/csse/research/COCOMOII/cocomo2000.0/CII_modelman2000.0.pdf}{Document link}
\end{itemize}
%