\section{Integration Strategy}
This section explains the integration strategy selected to integrate all the software elements of \myTaxiService{}.

\subsection{Entry Criteria}
%TODO Specify the criteria that must be met before integration testing of specific elements may begin (e.g., functions must have been unit tested).
Before starting the integration testing of any software component that has been designed for \myTaxiService{} system, the internal functions of the considered component (i.e. public or protected methods that are exposed within the package of the component but are not part of any external public interface) must be unit tested using \textbf{JUnit} framework.

\subsection{Elements to be Integrated}
%TODO Identify the components to be integrated, refer to your design document to identify such components in a way that is consistent with your design
Every software component in the Component View section of the Design Document has to be integrated.
The interested components are reported below for readers' convenience:
\begin{itemize}
	\item Passenger View
	\begin{itemize}
		\item PS Application View
		\item PS Web View
		\item PS Request Creator
		\item PS Receiver
	\end{itemize}
	\item Taxi Driver View
	\begin{itemize}
		\item TD Application View
		\item TD Request Creator
		\item TD Receiver
		\item TD Locator
		\item GPS Data Source
	\end{itemize}
	\item Administrator View
	\item Controller
	\begin{itemize}
		\item RESTful Service
		\item Dispatcher
		\item Location Manager
		\item Session Manager
		\item Profile Manager
		\item Taxi Driver Manager
		\item Taxi Ride Manager
		\item Queue Manager
		\item Taxi Sharing Manager
		\item Query Manager
	\end{itemize}
	\item Model
	\begin{itemize}
		\item Model Query Service
		\item Passenger DB Adapter
		\item Taxi Ride DB Adapter
		\item Zone DB Adapter
		\item Queue DB Adapter
		\item Database Driver Adapter
	\end{itemize}
\end{itemize}
Moreover we suppose that Google Maps API are well tested by Google and thus we can use them without testing any further.
For what concerns the other external software elements, we assume that the GPS Data Source module in the Taxi Driver View uses the GPS Drivers of the underlying operating system that are already tested, and the same is assumed for the Database Driver Adapter in the Model referring to Database Drivers.
Last but not least, \myTaxiService{} Taxi Sharing API will be tested in a separate environment using \textbf{JUnit} after the whole procedure indicated in this document has been completed.

\subsection{Integration Testing Strategy}
%TODO Describe the integration testing approach (top-down, bottom-up, functional groupings, etc.) and the rationale for the choosing that approach
The bottom-up integration testing approach has been chosen, because for a medium sized project like \myTaxiService{}, it is best to proceed step by step in a careful yet coherent integration strategy.
The usage of the selected approach will forge a robust application with efforts concentrated in testing the \textbf{Server} parts before all.
Therefore, a more stable and faster application will be distributed, instead of a maybe nicer one.

\subsection{Sequence of Component/Function Integration}
%TODO Note: The structure of this section may vary depending on the integration strategy you select in Section 2.3. Use the structure proposed below as a non mandatory guide.
Here is presented how the bottom-up integration testing approach is going to be concretely used in \myTaxiService{} system integration, first by analyzing each subsystem in detail and then giving a higher level overview on the subsystems integration process.
A precise convention has been adopted for the semantic of diagrams:
\begin{itemize}
	\item
		\textbf{Block:}
		\begin{itemize}
			\item \textbf{Yellow:} This block is not dependent on any lower level component in \myTaxiService{} and therefore it is integrated as a starting point in the current diagram.
			\item \textbf{Blue:} This block is going to be fully integrated on the top of any ancestor block in the diagram, and depends directly on its parents.
			\item \textbf{Green:} This block can only be the father of a blue or brown block because, in a previous diagram (i.e. integration step) it has been fully integrated within the system.
			Therefore it can be used to integrate other components on the top of it, as children in the diagram.
			\item \textbf{Brown:} This block is not going to be fully integrated within the current diagram (i.e. integration step), but only a subset of its functionalities are going to be tested.
			\item \textbf{Red:} This block represents a stub component, that replaces the real component mocking its functionalities.
			It's a trick made necessary by the fact that some components are going to be integrated before some other needed components have been integrated, and therefore they require a stub in order to work.
			The component represented by a red block is going to be integrated afterwards.
		\end{itemize}
	\item
		\textbf{Arrow:} Starts from a block and ends into another block.
		The block from which it is starting is called parent and the other one child.
		To cross an arrow in the diagram means that you are integration testing the parent exposed interfaces used by the child.
	\item
		\textbf{Blocks Visiting Order:} Each block can be traversed only once.
		The starting arrows from a block can be traversed in parallel, when the arrows from all the parent of the considered block have been traversed.
		A block without incoming arrows can be used as a start for a new path as soon as possible.
		A diagram is completed when all the possible path have been traversed.
\end{itemize}

\newpage
\subsubsection{Subsystem Integration Sequence}
%TODO Identify the order in which subsystems will be integrated. If you have a single subsystem, 2.4.1 and 2.4.2 are to be merged in a single section. You can refer to Section 2.2 of the test plan example [1] as an example of what we expect.

We adopted a \textbf{bottom-up} testing strategy; this strategy starts from the testing of the \textbf{Model} features.

\begin{center}
	\begin{tikzpicture}[node distance=2cm, auto]
		% Place nodes
		\node [block, fill=yellow!20] (model) {Model};
		\node [block, right of=model, node distance=2.5cm] (controller) {Controller};
		\node [block, right of=controller, node distance=3cm] (passenger_view) {Passenger View};
		\node [block, above of=passenger_view] (taxi_driver_view) {Taxi Driver View};
		\node [block, below of=passenger_view] (administrator_view) {Administrator View};
		% Draw edges
		\path [line] (model) -- (controller);
		\path [line] (controller) -- (passenger_view);
		\path [line] (controller) |- (taxi_driver_view);
		\path [line] (controller) |- (administrator_view);
	\end{tikzpicture}
	\captionof{figure}{Software Integration Sequence Diagram}
\end{center}

We considered \textbf{Model}, \textbf{Controller} and \textbf{Views} as \textbf{Subsystems}.
First the \textit{tester} has to test \textit{functionalities} of the components contained in the \textbf{Model}, then, in order to simulate the behavior of the interacting software elements, he has to represent the \textbf{Controller} with a dedicated \textbf{Driver} in order to test the relevant \textbf{Model} features.
In this way, the \textbf{Model} will be completely integration tested by simulating all the possible actions that the \textbf{Controller} can do on it.\par
Then the testing procedure passes to the \textbf{Controller} and the test sequence adopts the same strategy used to test the \textbf{Model}. The only difference from a higher point of view, is that in this case the \textbf{Controller} is tested using the already tested \textbf{Model} and using a \textbf{Driver} in order to simulate the \textbf{Views} actions.\par
The last part of the procedure is dedicated to the \textbf{Views}.
The \textbf{Taxi Driver View, Passenger View and Administrator View} are tested using the already tested \textbf{Controller} and \textbf{Model} and no component behavior is simulated using \textbf{Stubs} or \textbf{Drivers}.

\newpage
\subsubsection{Software Integration Sequence}
%TODO For each subsystem: Identify the sequence in which the software components will be integrated within the subsystem. Relate this sequence to any product features/functions that are being built up

\paragraphnewline{Model Integration Sequence}
\begin{center}
	\begin{tikzpicture}[node distance=2cm, auto]
		% Place nodes
		\node [block, fill=yellow!20] (datbase_driver_adapter) {Database Driver Adapter};
		\node [block, right of=datbase_driver_adapter, node distance=5cm] (taxi_driver_db_adapter) {Taxi Driver DB Adapter};
		\node [block, above of=taxi_driver_db_adapter] (taxi_ride_db_adapter) {Taxi Ride DB Adapter};
		\node [block, above of=taxi_ride_db_adapter] (passenger_db_adapter) {Passenger DB Adapter};
		\node [block, below of=taxi_driver_db_adapter] (zone_db_adapter) {Zone DB Adapter};
		\node [block, below of=zone_db_adapter] (queue_db_adapter) {Queue DB Adapter};
		\node [block, right of=taxi_driver_db_adapter, node distance=5cm, fill=green!20] (model_query_service) {Model Query Service};
		% Draw edges
		\path [line] (datbase_driver_adapter) -- (taxi_driver_db_adapter);
		\path [line] (datbase_driver_adapter) |- (taxi_ride_db_adapter);
		\path [line] (datbase_driver_adapter) |- (passenger_db_adapter);
		\path [line] (datbase_driver_adapter) |- (zone_db_adapter);
		\path [line] (datbase_driver_adapter) |- (queue_db_adapter);
		\path [line] (taxi_driver_db_adapter) -- (model_query_service);
		\path [line] (taxi_ride_db_adapter) -| (model_query_service);
		\path [line] (passenger_db_adapter) -| (model_query_service);
		\path [line] (zone_db_adapter) -| (model_query_service);
		\path [line] (queue_db_adapter) -| (model_query_service);
	\end{tikzpicture}
	\captionof{figure}{Software Integration Sequence Diagram - Model}
\end{center}

\paragraphnewline{Controller Business Components Integration Sequence}
\begin{center}
	\begin{tikzpicture}[node distance=2cm, auto]
		% Place nodes
		\node [block, fill=green!20] (query_manager) {Query Manager};
		\node [block, above of=query_manager, fill=green!20] (model_query_service) {Model Query Service};
		\node [block, below of=query_manager] (taxi_sharing_manager) {Taxi Sharing Manager};
		\node [block, left of=taxi_sharing_manager, node distance=3.5cm, fill=green!20] (profile_manager) {Profile Manager};
		\node [block, left of=query_manager, node distance=3.5cm, fill=green!20] (session_manager) {Session Manager};
		\node [block, right of=taxi_sharing_manager, node distance=3.5cm] (location_manager) {Location Manager};
		\node [block, above of=location_manager, fill=red!20] (taxi_driver_view_stub) {TD Locator Stub};
		\node [block, below of=location_manager, fill=green!20] (taxi_ride_manager) {Taxi Ride Manager};
		\node [block, below of=taxi_sharing_manager, fill=green!20] (queue_manager) {Queue Manager};
		\node [block, left of=queue_manager, fill=red!20, node distance=3.5cm] (dispatcher_stub) {Dispatcher Stub};
		\node [block, below of=queue_manager, fill=green!20] (taxi_driver_manager) {Taxi Driver Manager};
		% Draw edges
		\path [line] (model_query_service) -- (query_manager);
		\path [line] (query_manager) -- (taxi_sharing_manager);
		\path [line] (query_manager) -- (profile_manager);
		\path [line] (query_manager) -- (session_manager);
		\path [line] (query_manager) -- (location_manager);
		\path [line] (taxi_driver_view_stub) -- (location_manager);
		\path [line] (location_manager) -- (queue_manager);
		\path [line] (dispatcher_stub) -- (queue_manager);
		\path [line] (dispatcher_stub) -- (taxi_driver_manager);
		\path [line] (location_manager) -- (taxi_ride_manager);
		\path [line] (queue_manager) -- (taxi_driver_manager);
	\end{tikzpicture}
	\captionof{figure}{Software Integration Sequence Diagram - Controller Business Components}
\end{center}

\paragraphnewline{Controller Networking Components Integration Sequence}
\begin{center}
	\begin{tikzpicture}[node distance=2cm, auto]
		% Place nodes
		\node [block, fill=green!20] (dispatcher) {Dispatcher};
		\node [block, above of=dispatcher, fill=red!20] (td_view_stub) {TD Receiver Stub};
		\node [block, below of=dispatcher, fill=red!20] (passenger_view_stub) {PS Receiver Stub};
		\node [block, right of=td_view_stub, node distance=4cm, fill=green!20] (queue_manager) {Queue Manager};
		\node [block, below of=queue_manager, fill=green!20] (taxi_driver_manager) {Taxi Driver Manager};
		\node [block, below of=taxi_driver_manager, fill=green!20] (session_manager) {Session Manager};
		\node [block, right of=taxi_driver_manager, node distance=4cm, fill=green!20] (restful_service) {RESTful Service};
		\node [block, below of=restful_service, fill=green!20] (profile_manager) {Profile Manager};
		\node [block, above of=restful_service, fill=green!20] (taxi_ride_manager) {Taxi Ride Manager};		
		% Draw edges
		\path [line] (taxi_driver_manager) -- (restful_service);
		\path [line] (taxi_ride_manager) -- (restful_service);
		\path [line] (session_manager) -- (restful_service);
		\path [line] (profile_manager) -- (restful_service);
		\path [line] (dispatcher) -- (taxi_driver_manager);
		\path [line] (dispatcher) -- (queue_manager);
		\path [line] (td_view_stub) -- (dispatcher);
		\path [line] (passenger_view_stub) -- (dispatcher);
	\end{tikzpicture}
	\captionof{figure}{Software Integration Sequence Diagram - Controller Networking Components}
\end{center}

\paragraphnewline{Passenger View Integration Sequence}
\begin{center}
	\begin{tikzpicture}[node distance=2cm, auto]
		% Place nodes
		\node [block] (psreq) {PS Request Creator};
		\node [block, fill=green!20, left of=psreq, node distance=3.5cm] (restful_service) {RESTful Service};
		\node [block, right of=psreq, above of=psreq] (psw) {PS Web View};
		\node [block, right of=psreq, below of=psreq] (papp) {PS Application View};
		\node [block, below of=psw, right of=psw] (psr) {PS Receiver};
		\node [block, right of=psr, fill=green!20, node distance=2.5cm] (dp) {Dispatcher};
		% Draw edges
		\path [line] (restful_service) -- (psreq);
		\path [line] (psreq) |- (psw);
		\path [line] (psreq) |- (papp);
		\path [line] (psw) -| (psr);
		\path [line] (papp) -| (psr);
		\path [line] (psr) -- (dp);
	\end{tikzpicture}
	\captionof{figure}{Software Integration Sequence Diagram - Passenger View}
\end{center}

\paragraphnewline{Taxi Driver View Integration Sequence}
\begin{center}
	\begin{tikzpicture}[node distance=4.5cm, auto]
		% Place nodes	
		\node [block] (treq) {TD Request Creator};
		\node [block, above of=treq, fill=green!20, node distance=2cm] (rs) {RESTful Service};
		\node [block, right of=treq] (tapp) {TD Application View};
		\node [block, right of=tapp] (tr) {TD Receiver};
		\node [block, below of=treq, node distance=2cm,, fill=yellow!20] (gps) {GPS Data Source};
		\node [block, right of=gps] (tl) {TD Locator};
		\node [block, below of=tr, fill=green!20, node distance=2cm] (dispatcher) {Dispatcher};
		% Draw edges
		\path [line] (rs) -- (treq);
		\path [line] (treq) -- (tapp);
		\path [line] (tapp) -- (tr);
		\path [line] (gps) -- (tl);
		\path [line] (tr) -- (dispatcher);
		\path [line] (tl) -- (dispatcher);
	\end{tikzpicture}
	\captionof{figure}{Software Integration Sequence Diagram - Taxi Driver View}
\end{center}

\paragraphnewline{Administrator View Integration Sequence}
\begin{center}
	\begin{tikzpicture}[node distance=2cm, auto]
		% Place nodes	
		\node [block, fill=green!20] (qm) {Query Manager};
		\node [block, right of=qm, node distance=4cm] (admw) {Administrator View};
		% Draw edges
		\path [line] (qm) -- (admw);
	\end{tikzpicture}
	\captionof{figure}{Software Integration Sequence Diagram - Administrator View}
\end{center}