\documentclass{../common/latex_classes/pdf_presentation}

\title{ID Presentation}

\subject{A brief presentation of the Inspection Document}
% This is only inserted into the PDF information catalog. Can be left
% out. 

% Let's get started
\begin{document}
	\titleToc{}
	\section{Class Name and Pattern Explanation}
	
	\begin{frame}{IIOPSSLSocketFactory - Overview}
		The class we have been assigned is named \textbf{IIOPSSLSocketFactory}.
		It is included in the \textbf{org.glassfish.enterprise.iiop.impl} package.
		\textbf{IIOPSSLSocketFactory} implements the \textbf{ORBSocketFactory} interface, which is part of the \textbf{CORBA} (Common Object Request Broker Architecture) standard declined to \textbf{Java Enterprise Edition}.
	\end{frame}
	
	\begin{frame}{IIOPSSLSocketFactory - ORB}
		The \textbf{ORBSocketFactory} interface is included in the \textbf{com.sun.corba.ee.spi.transport} package, and is an interface that abstracts some parts of the \textbf{ORB} (Object Request Broker) middleware related to sockets creation.
		As the name suggests, the \textbf{ORBSocketFactory} interface is a \textbf{Factory} of \textbf{Sockets} for the \textbf{ORB} middleware.
	\end{frame}
	
	\begin{frame}{IIOPSSLSocketFactory - IIOP}
		The \textbf{IIOP} (Internet Inter-ORB Protocol, a concrete protocol) is an implementation of the \textbf{GIOP} (General Inter-ORB Protocol, an abstract protocol) that \textbf{ORB}s use to communicate over the Internet, and provides a mapping between \textbf{GIOP} messages and the \textbf{TCP/IP} layer.
		Our class is therefore a \textbf{Factory} of \textbf{SSLSockets} for \textbf{IIOP}, and is an \textbf{Implementation} of the relevant part of the \textbf{IIOP} included in the \textbf{Enterprise} facilities of the \textbf{GlassFish} server.
	\end{frame}
	
	\section{Functional Role of Assigned Class}
	
	\subsection{Class Issues}
	
	\begin{frame}{Class Issues - Overview}
		In this subsection are listed the issues related to the whole class and not only to a specific method. \par Below we propose only few \textbf{selected}, \textbf{particular} and \textbf{meaningful} issues that we have thought could have been interesting to be spoken about.
	\end{frame}
	\begin{frame}{Class Issues - Checklist[1] Naming Conventions}
		The class has the capability of creating also \textbf{Plain Text Socket} and \textbf{Plain Text Server Socket}, even if the name \textbf{IIOPSSLSocketFactory} clearly underlines that the class has to be a Factory of \textbf{Secure Sockets and Server Sockets}. In order to give the architecture the ability of creating \textbf{Plain Text Socket} and \textbf{Plain Text Server Socket}, a separate class has to be thought.
	\end{frame}
	
	\subsection{Method Issues}
	
