\section{Requirements Traceability}
In this section are mapped all the functional requirements identified in the \textbf{RASD}, grouped by the \textbf{Use Case} they refer to.

\subsection{Registration}
\reqTracTab{
	FR1, FR2 &
	%A non registered passenger can register only once.
	The \textbf{Profile Manager} perform data validation and checks if the passenger is already registered to \myTaxiService{}. \\
	\hline
	FR3 &
	%In no case can a registration process be resumed after browser or application closure.
	The registration process is handled as an atomic procedure by the \textbf{Profile Manager}: if the registration process is stopped, there are no choices of resuming. \\
	\hline
	FR4 &
	%The system must acknowledge the non registered passenger whether the registration process ends successfully or fails.
	Through the response to the registration request sent to the \textbf{RESTful Service}, the passenger is informed about the result of the process. \\
	\hline
	FR5 &
	%The system must send an email to the non registered passenger that has completed the registration.
	Through an internal method of the \textbf{Profile Manager} is possible to send an email to the just registered \textbf{Passenger}. \\
	\hline
	FR6 &
	%After the registration is completed successfully, the non registered passenger involved in the process must be considered a registered passenger.
	If the registration process is completed successfully, then the \textbf{Profile Manager} has to call a method of the \textbf{Query Passenger Model} in order to make the registration effective and persistent. From this moment, if that Passenger tries to login, the system must recognize him as a user of the service and allow him to use all the features of \myTaxiService{}. \\
}

\subsection{Login}
\reqTracTab{
	FR7 &
	%The system must check the correctness of the user's inserted data.
	The validation of Passenger inserted data is done by the \textbf{Session Manager} after checking for a possible duplication of the user session. \\
	\hline
	FR8 &
	%The system must correctly handle internally the login token assignment to the user.
	The \textbf{Session Manager} generates the Login Token once it is sure of the correctness of the login data, and associates it to the user via the \textbf{Query Manager}. \\
	\hline
	FR9 &
	%The system must notify the user about the result of his login.
	The notification of the result of the login procedure is produced in the \textbf{Session Manager} and sent as response to the user that requested the login. \\
	\hline
	FR10 &
	%The system must peacefully handle a connection error and notify the user of the problem.
	The \textbf{PS Request Creator}, \textbf{TD Request Creator} and the \textbf{RESTful Service} are capable of handling connection errors without making the relevant systems crash. \\
	%The internal software architecture of the \textbf{Session Manager} is built in order to catch exceptions and to handle them in a proper way. \\	
	%The \textbf{Point to Point} communication channel is used for delivering from the \textbf{Server} to the \textbf{Client} some notification about error's state. \\
}

\subsection{Logout}
\reqTracTab{
	FR11 &
	%The system must offer the possibility to logout to a given RP.
	The Passenger can perform the Logout procedure by interacting with the \textbf{PS Web View} or \textbf{PS Application View}. \\
	\hline
	FR12 &
	%After the logout, the system must redirect the RP to the \myTaxiService{} home page.
	All the logic about the navigation inside the application and in general about the building of the View is contained into the \textbf{PS Web View} or \textbf{PS Application View}. \\
	%It is defined through client side languages such as \textbf{Javascript} or \textbf{HTML} directives.
	\hline
	FR13 &
	%The system must peacefully handle a connection error and notify the user of the problem.
	The \textbf{PS Request Creator}, \textbf{TD Request Creator} and the \textbf{RESTful Service} are capable of handling connection errors without making the relevant systems crash. \\
	%The internal software architecture of the \textbf{PS Web View} or \textbf{PS Application View} is built in order to catch exceptions and to handle them in a proper way. \\
	%The \textbf{Point to Point} communication channel is used for delivering from the \textbf{Server} to the \textbf{Client} some notification about error's state. \\
}

\subsection{View Request and Reservations}
\reqTracTab{
	FR14 &
	%The system must be capable of loading a given RP data at any time.
	The data is accessible through the \textbf{Query Manager}, that calls the \textbf{Model Query Service} to reach the \textbf{Passenger DB Adapter}. \\
	\hline
	FR15 &
	%The system must ask a RP for cancel confirmation before actually canceling a taxi ride.
	\textbf{PS Application View} and \textbf{PS Web View} handle this interface logic. \\
	\hline
	FR16 &
	%A message must be displayed in place of an empty list in case there's not Taxi Request to display or in case the Taxi Reservations list is empty for a given RP.
	\textbf{PS Application View} and \textbf{PS Web View} handle this interface logic. \\
	\hline
	FR17 &
	%The system must peacefully handle a connection error and notify the user of the problem.
	The \textbf{PS Request Creator} and the \textbf{RESTful Service} are capable of handling connection errors without making the relevant systems crash. \\
}

\subsection{Handle Personal Profile}
\reqTracTab{
	FR18 & 
	%The system must check the correctness of a RP's inserted data.
	This validation is done by the \textbf{Profile Manager}. \\
	\hline
	FR19 &
	%The system must be coherent with the RP inserted data modification, if the modification goes fine.
	The \textbf{Profile Manager} uses the interfaces exposed by the \textbf{Query Manager} to guarantee so. \\
	\hline
	FR20 &
	%The system must inform a RP about the result of his modification.
	This information is sent as a response to a profile modification request by the \textbf{RESTful Service} \\
	\hline
	FR21 &
	%The system must peacefully handle a connection error and notify the user of the problem.
	The \textbf{PS Request Creator} and the \textbf{RESTful Service} are capable of handling connection errors without making the relevant systems crash. \\
}

\subsection{Taxi Reservation}
\reqTracTab{
	FR22 &
	%The system must check the correctness of the RP's inserted data.
	This validation is done by the \textbf{Taxi Ride Manager}. \\
	\hline
	FR23 &
	%The system must correctly handle internally the added taxi reservation.
	The \textbf{Taxi Ride Manager} uses the interfaces exposed by the \textbf{Query Manager} to guarantee so. \\
	\hline
	FR24 &
	%The system must notify the RP about the result of his operation.
	This information is sent as a response to a Taxi Reservation request by the \textbf{RESTful Service} \\
	\hline
	FR25 &
	%The system must peacefully handle a connection error and notify the user of the problem.
	The \textbf{PS Request Creator} and the \textbf{RESTful Service} are capable of handling connection errors without making the relevant systems crash. \\
}

\subsection{Taxi Request}
\reqTracTab{
		FR26 &
		%The system must check the data inserted by a RP into the Request a Ride Page and notify the RP in case of problems.
		Data validation is done by the \textbf{Taxi Ride Manager}. If the data don't respect the constraints, then the \textbf{Taxi Ride Manger} informs the related Passenger of the issue. \\
		\hline
		FR27 &
		%The system must correctly handle internally a taxi ride that is successfully issued by a RP.
		When a Passenger sends a Taxi Ride request to \myTaxiService{}, the \textbf{RESTful Service} handles it.
		Then the \textbf{Taxi Ride Manager} completes the \textbf{Taxi Ride} request by adding the Zone of the Starting Address.
		In addition, this component keeps the model updated by adding the ride to the persistent data layer.
		Later on the \textbf{Queue Manager} picks the ride from the Model and associates it to a Taxi Driver.
		In conclusion this component uses the \textbf{Dispatcher} to notify the Passenger with notification message that contains the Taxi Driver ID and Travel Time. \\
		\hline
		FR28 &
		%The RP must be notified about the result of his request.
		Through the \textbf{Dispatcher}, users can be reached in every moment by notification messages. \\
		\hline
		FR29 &
		%The system must peacefully handle a connection error and notify the user of the problem.
		%The internal software architecture of the \textbf{Taxi Ride Manager} is built in order to catch exceptions and to handle them in a proper way. 
		%The \textbf{Point to Point} communication channel is used for delivering some notification about error's state from the \textbf{Server} to the \textbf{Client}. \\
		The \textbf{PS Request Creator}, the \textbf{PS Receiver}, the \textbf{RESTful Service} and the \textbf{Dispatcher} are capable of handling connection errors without making the relevant systems crash. \\
}

\subsection{Notify Problem}
\reqTracTab{
	FR30 &
	%The system must offer the possibility to report a problem with a dedicated text area and a combo box to specify whether the problem is solvable without interrupting the taxi driver's work.
	The \textbf{TD Application View} is provided with a specific screen that allows the Taxi Driver to report a problem.
	In addition, Taxi Driver has a chance to specify whether or not he can solve the given problem
	These data are then sent to the \textbf{RESTful Service} in order to be processed by the \textbf{Taxi Driver Manager}. \\
	\hline
	FR31 &
	%The system must be capable of automatically issuing a new taxi request for the passenger that is involved in a non solvable problem during his taxi ride.
	This task is done by the \textbf{Taxi Driver Manager}. \\
	\hline
	FR32 &
	%The system must be capable of notifying Amy about the result of her problem reporting.
	This is sent a response to a Notify Problem request by the \textbf{RESTful Service}. \\
	\hline
	FR33 &
	%The system must be capable of notifying Frank about the evolving of his automatically issued request.
	This is done by the \textbf{Taxi Driver Manager} via the \textbf{Dispatcher}. \\
	\hline
	FR34 &
	%The system must peacefully handle a connection error and notify the user of the problem.
	%The internal software architecture of the \textbf{Taxi Driver Web or Application View} is built in order to catch exceptions and to handle them in a proper way. 
	%The \textbf{Point to Point} communication channel is used for delivering some notification about error's state from the \textbf{Server} to the \textbf{Client}. \\
	The \textbf{TD Request Creator}, the \textbf{TD Receiver}, the \textbf{RESTful Service} and the \textbf{Dispatcher} are capable of handling connection errors without making the relevant systems crash. \\
}
	
\subsection{End of Ride}
\reqTracTab{
		FR35 & 
		%A taxi driver must be capable of notifying the end of a taxi ride he is serving.
		The Taxi Driver pushes a button on the \textbf{TD Application View} that calls the \textbf{TD Request Creator}, which sends a request to the \textbf{RESTful Service}. The request is then forwarded to the \textbf{Taxi Ride Manager} by the \textbf{RESTful Service}. The \textbf{Taxi Ride Manager} handles the operation. \\
		\hline
		FR36 &
		%The system must automatically re-enqueue the taxi driver that notifies the end of his current taxi ride in the queue of his current zone.
		When a Taxi Driver has notified the end of his current Taxi Ride, he is associated to a Available status. Then the \textbf{Queue Manager} is waiting for Taxi Drivers to become Available to enqueue them into their current Zone. \\
		\hline
		FR37 &
		%A notification must be sent from the system to the taxi driver to inform him about the result of his action.
		The response to the request made to achieve FR35 contains the result of the \textbf{Taxi Driver} action. \\
		\hline
		FR38 &
		%The system must peacefully handle a connection error and notify the user of the problem.
		The \textbf{TD Request Creator} and the \textbf{RESTful Service} are capable of handling connection error problem without making the relevant systems crash. \\
}
