\section{Introduction}
This section contains a brief but complete introduction of \myTaxiService{} Design Document.

\subsection{Purpose}
The purpose of this document is to explain the Design and Architectural elements that characterize \myTaxiService{} as a software system. The level of the description is high enough for all the stakeholders to capture the information they need in order to decide whether the system meets their requirements or in order to begin the development work.

\subsection{Scope}
This document provides a detailed description of \myTaxiService{} software design and architectural choices.
It consists in natural language descriptions, UML Diagrams and portions of Java code, proposed in a way that should be clear and direct.
Every portion of the document is designed itself to be comprehensible, but a big picture of the system must be present to the reader in order to obtain the best knowledge on the matter when consulting this document.

\subsection{Definitions, Acronyms, Abbreviations}
In the document are often used some technical terms whose definitions are here reported:
\begin{itemize}
	\itemBold{Layer} A software level in a software system.
	\itemBold{Tier} An hardware level in a software system.
	\itemBold{Relational Database} A digital database whose organization is based on the relational model of data, as proposed by E.F. Codd in 1970.
	\itemBold{Cocoa MVC} A strict application of MVC principles.
	\item See the correspondent section in the \textbf{RASD} for more definitions.
\end{itemize}
For sake of brevity, some acronyms and abbreviations are used:
\begin{itemize}
	\itemBold{DD} Design Document.
	\itemBold{GPS} Global Positioning System.
	\itemBold{GUI} Graphic User Interface.
	\itemBold{API} Application Programming Interface.
	\itemBold{MVC} Model View Controller.
	\itemBold{ETA} Estimated Time of Arrival.
	\item See the correspondent section in the \textbf{RASD} for more acronyms and abbreviations.
\end{itemize}

\subsection{Reference Documents}
This document contains references to:
\begin{itemize}
	\itemBold{\myTaxiService{} RASD}  Requirements Analysis and Specification Document for \myTaxiService{}
	\itemBold{IEEE Std 1016-2009} IEEE Standard for Information Technology - Systems Design - Software Design Descriptions
	\itemBold{ISO/IEC/IEEE 42010} International Standard for Systems and software engineering - Architecture description
\end{itemize}

\subsection{Document Structure}
This document is divided in 4 main sections:
\begin{itemize}
	\itemBold{Architectural Design} This section exposes in details the design chosen for the architecture of the system to be, using user friendly diagrams, UML Diagrams and natural language.
	\itemBold{Algorithm Design} Here are exposed some of the algorithms that have been designed in order for the application to work in the desired way.
		Some Java code is used to show in a more coherent, correct and meaningful way such algorithms.
	\itemBold{User Interface Design} In this section are presented some mockups of the system that is going to be developed. In particular, we are presenting mockups for the four GUIs:
	\begin{itemize}
		\item Passenger Web
		\item Passenger Mobile
		\item Taxi Driver Mobile
		\item Administrator Workstation
	\end{itemize}
	\itemBold{Requirements Traceability} In this part of the document are mapped the requirements that were discovered in the RASD to design and architectural decisions.
\end{itemize}