\section{Function Points and COCOMO}
%TODO Apply Function Points to estimate the project size and then COCOMO to estimate effort and cost.
%TODO 1) table for weights
%TODO 1.2) describe 
%TODO ext input
%TODO ext ouput
%TODO etc
%TODO for each task asssign a level of complexity
%TODO 2) COCOMO
%TODO use free tools online (logo tipo tempio greco)
%TODO 3) describe the number of hours spent for the various tasks (RASD, DD etc.)
\subsection{Function Points}
\begin{center}
	\begin{tabulary}{\linewidth\tymin=70pt}{Y{2cm}|Y{1.75cm}|Y{1.75cm}|Y{1.75cm}}
		\textbf{Function\newline{}Types} & \textbf{Simple\newline{}Weight} & \textbf{Medium\newline{}Weight} & \textbf{Complex\newline{}Weight} \\ \hline
		N. Inputs & 3 & 4 & 6 \\ \hline
		N. Outputs & 4 & 5 & 7 \\ \hline
		N. Inquiry & 3 & 4 & 6 \\ \hline
		N. ILF & 7 & 10 & 15 \\ \hline
		N. ELF & 5 & 7 & 10 \\
	\end{tabulary}
\end{center}
\subsubsection{Internal Logic File}
Summary of the calculated weights:
\begin{equation*}
	\begin{aligned}
		&	FP_{ILF}
		& & = 9 \cdot w_{Simple,ILF} + 1 \cdot w_{Medium,ILF}\\
		&&& = 9 \cdot 7 + 1 \cdot 10\\
		&&& = 73\\
	\end{aligned}
\end{equation*}
In details:
\begin{itemize}
	\fp{Registered Passenger}{Personal Registered Passenger data. Infrequent modifications, but frequent insertions and readings.}{1}{w_{Simple,ILF}}
	\fp{Taxi Driver}{Taxi Driver data. Very infrequent modifications, infrequent insertions, frequent readings.}{1}{w_{Simple,ILF}}
	\fp{Administrator}{Administrator data. Very infrequent modifications, insertions and readings.}{1}{w_{Simple,ILF}}
	\fp{Taxi Car}{Taxi Car data. Very infrequent modifications, insertions and readings.}{1}{w_{Simple,ILF}}
	\fp{Taxi Request}{Taxi Request data. Frequent insertions and readings, infrequent modifications.}{1}{w_{Simple,ILF}}
	\fp{Taxi Reservation}{Taxi Reservation data. Frequent insertions and readings, infrequent modifications.}{1}{w_{Simple,ILF}}
	\fp{Problem}{Problem data. Infrequent insertions, readings and modifications.}{1}{w_{Simple,ILF}}
	\fp{Zone}{Zone data. Very infrequent insertions, readings and modifications.}{1}{w_{Simple,ILF}}
	\fp{GPS Data}{GPS Data, Database Server side. Very frequent insertions and readings, but very infrequent modifications.}{1}{w_{Medium,ILF}}
	\fp{Taxi Drivers Queue}{Taxi Drivers Queue data. Frequent insertions, readings and modifications.}{1}{w_{Simple,ILF}}
\end{itemize}
\subsubsection{External Interface File}
Summary of the calculated weights:
\begin{equation*}
	\begin{aligned}
		&	FP_{ELF}
		& & = 2 \cdot w_{Simple,ELF} + 1 \cdot w_{Medium,ELF}\\
		&&& = 2 \cdot 5 + 1 \cdot 7\\
		&&& = 17\\
	\end{aligned}
\end{equation*}
In details:
\begin{itemize}
	\fp{Google Maps API}{Google Maps API related data about Travel Time and Addresses. Very frequent readings.}{2}{w_{Simple,ELF}}
	\fp{GPS Data}{GPS Data, Taxi Driver side. Very frequent insertions and readings, but very infrequent modifications.}{1}{w_{Medium,ELF}}
\end{itemize}
\subsubsection{External Input}
Summary of the calculated weights:
\begin{equation*}
	\begin{aligned}
		&	FP_{EI}
		& & = 4 \cdot w_{Simple,EI} + 3 \cdot w_{Medium,EI} + 1 \cdot w_{Complex,EI}\\
		&&& = 4 \cdot 3 + 3 \cdot 4 + 1 \cdot 6\\
		&&& = 30\\
	\end{aligned}
\end{equation*}
In details:
\begin{itemize}
	\fp{Login}{This operation requires a simple effort. In fact it has to perform few steps in order to conclude the procedure.}{1}{w_{Simple,EI}}
	\fp{Logout}{This operation requires a simple effort. In fact it has to perform few steps in order to conclude the procedure.}{1}{w_{Simple,EI}}
	\fp{Registration}{This operation requires a simple effort. In fact it has to perform few steps in order to conclude the procedure.}{1}{w_{Simple,EI}}
	\fp{Handle Personal Profile}{This operation requires a simple effort. In fact it has to perform few steps in order to conclude the procedure.}{1}{w_{Simple,EI}}
	\fp{Taxi Reservation}{This operation requires a medium effort. In fact it is very frequent.}{1}{w_{Medium,EI}}
	\fp{Taxi Request}{This operation requires a medium effort. In fact it is very frequent.}{1}{w_{Medium,EI}}
	\fp{Notify Problem}{This operation requires a strong effort. In fact it has to perform many elementary steps in order to handle the problem.}{1}{w_{Complex,EI}}
	\fp{End of Ride}{This operation requires a medium effort. In fact it is very frequent.}{1}{w_{Medium,EI}}
\end{itemize}
\subsubsection{External Output}
Summary of the calculated weights:
	\begin{equation*}
		\begin{aligned}
		&	FP_{EO}
		& & = 9 \cdot w_{Simple,EO} + 1 \cdot w_{Complex,EO}\\
		&&& = 9 \cdot 4 + 1 \cdot 7\\
		&&& = 43\\
	\end{aligned}
\end{equation*}
In details:
\begin{itemize}
	\fp{Logout}{A redirection message needs to be sent to the user that logs out.}{1}{w_{Simple,EO}}
	\fp{Registration}{The result of this operation must be sent to the user that registers}{1}{w_{Simple,EO}}
	\fp{Login}{The result of the login must be sent to the specific user.}{1}{w_{Simple,EO}}
	\fp{Handle Personal Profile}{Informations about the result of the modification must be sent to the related user}{1}{w_{Simple,EO}}
	\fp{Taxi Reservation}{Notification about the result of the reservation must be sent to the specific passenger.}{1}{w_{Simple,EO}}
	\fp{Notify Problem}{Notification about the result of the request must be sent to the specific passenger.}{1}{w_{Simple,EO}}
	\begin{itemize}
		\fp{Automatic Taxi Request}{A new Taxi Request must be issued.}{1}{w_{Complex,EO}}
		\fp{Notification to the Passenger}{Notification about the new Taxi Request must be sent to the specific passenger.}{1}{w_{Simple,EO}}
		\fp{Notification to the Taxi Driver}{Notification about the result of the request must be sent to the specific Taxi Driver.}{1}{w_{Simple,EO}}
	\end{itemize}
	\fp{End of Ride}{Notification about the result of the operation must be sent to the relevant Taxi Driver.}{1}{w_{Simple,EO}}
\end{itemize}
\subsubsection{External Inquiry}
Summary of the calculated weights:
\begin{equation*}
	\begin{aligned}
		&	FP_{EIQ}
		& & = 2 \cdot w_{Simple,EIQ}\\
		&&& = 2 \cdot 3\\
		&&& = 6\\
	\end{aligned}
\end{equation*}
In details:
\begin{itemize}
	\fp{View Requests and Reservations}{In order to perform these operations the system has only to retrieve, send and render simple data.}{2}{w_{Simple,EIQ}}
\end{itemize}
\subsubsection{Summary}
To recap:
\begin{equation*}
	\begin{aligned}
		&	FP
		& & = FP_{ILF} + FP_{ELF} + FP_{EI} + FP_{EO} + FP_{EIQ}\\
		&&& = 73 + 17 + 30 + 43 + 6\\
		&&& = 169\\	
		\\
		&   n_{SLOC}
		& & = FP \cdot k_{Java, Avg}\\
		&&& = 169 \cdot 53\\
		&&& = 8957 \text{ SLOC}
	\end{aligned}
\end{equation*}

\subsection{COCOMO}
This estimation method takes into account a lot of parameters, such as final software, personnel and platform characteristics, combining them using a complex non-linear process.\\
In order to generate the \textbf{Constructive Cost Model} we decided to use the online \textbf{COCOMO II} tool, reachable at \href{http://csse.usc.edu/tools/COCOMOII.php}{http://csse.usc.edu/tools/COCOMOII.php}, using the \textbf{FP Sizing Method}.\\
We also used \href{http://csse.usc.edu/csse/research/COCOMOII/cocomo2000.0/CII_modelman2000.0.pdf}{COCOMO II - Model Definition Manual} to make better choices of the parameters we had to insert into the \textbf{model}.\\
\begin{itemize}
	\item \textbf{Software Size}
	\begin{itemize}
		\item \textbf{Unadjusted Function Points:} The value $FP$ has been taken as parameter, so $169$ is the value chosen for this field.
		\item \textbf{Language:} The language of choice is Java, and not only Java EE, because the software is possibly a combination of different flavours of Java (Java SE, Java EE and Java for Android).
	\end{itemize}
	\item Software Scale Drivers
	\begin{itemize}
		\itemBold{Precedentedness} Since we had a previous experience using \textit{Java SE} for medium-size projects, but we had never used \textit{Java EE} for developing such a big application we decided to set this parameter to \textbf{Nominal}.
		\itemBold{Development Flexibility} Given that we had not strict specifications we set this parameter to \textbf{High}.
		\itemBold{Architecture/Risk Resolution} %TODO
		\itemBold{Team Cohesion} After a few days dedicated to create a efficient and fast workspace, the cohesion reached an \textbf{Very High} level.
		\itemBold{Process Maturity} We understand, support and follow the process so we choose a \textbf{High} level for this parameter.
	\end{itemize}
	\item Software Cost Drivers
	\begin{itemize}
		\item Product
		\begin{itemize}
			\itemBold{Required Software Reliability}
			Given that a failure in the software system could lead to moderate problem we chose \textbf{Nominal} level.
			\itemBold{Data Base Size} Since we have a distributed application, the focus is on the lines of code instead of being on the size of the testing Database; so we chose a \textbf{Low} level parameter.
			\itemBold{Product Complexity} We made an average of the various complexity areas and we chose a \textbf{High} level parameter.
			\itemBold{Developed for Reusability} We decided to develop reusable system components, so we came up with an \textbf{High} level parameter.
			\itemBold{Documentation Match to Lifecycle Needs} The standard level of documentation is required, so the chosen level is \textbf{Nominal}.
		\end{itemize}
		\item Personnel
		\begin{itemize}
			\item Analyst Capability
			\item Programmer Capability
			\item Personnel Continuity
			\item Application Experience
			\item Platform Experience
			\item Language and Toolset Experience
		\end{itemize}
		\item Platform
		\begin{itemize}
			\itemBold{Time Constraint} We have no relevant time constraints, so we chose \textbf{Nominal} level for this parameter.
			\itemBold{Storage Constraint} We have no relevant storage constraint, so we chose \textbf{Nominal} level for this parameter. 
			\itemBold{Platform Volatility} Our hardware and software platforms do not change often, so we have no volatility and we chose a \textbf{Low} level for this constraint.
		\end{itemize}
		\item Project
		\begin{itemize}
			\item Use of Software Tools
			\item Multisite Development
			\item Required Development Schedule
		\end{itemize}
	\end{itemize}
	\item Maintenance
	\item Software Labor Rates
	\begin{itemize}
		\item Cost per Person-Month (Dollars)
	\end{itemize}	
\end{itemize}


%